Evaluation of Diagnostic Concordance Between Algorithms for Parkinson’s Disease Dementia

### 2025-10-08 _manuscript/manuscript.qmd
Added option to regress PDD on covariates, cleaned the code for the original text.

desc <- tar_read(sample_description, store = upstore)
rates <- tar_read(rate_summaries, store = upstore)
pred <- tar_read(demographic_predictors, store = upstore)
conc <- tar_read(concordance_statistics, store = upstore)
perc <- rates$table$perc

@@

# Minimum p-value of logistic regressions:
min_p <- subset(pred$values, quantity == "p-value")$estimate |>
  min() |>
  do_summary(3, "p")

# List of algorithms:
algos <- list(
  faq_tot = subset(rates$table, IADL == "FAQ > 7")$type,
  faq_9 = subset(rates$table, IADL == "FAQ 9 > 1")$type
)

continue <- !(any(algos$faq_tot %in% algos$faq_9) || any(algos$faq_9 %in% algos$faq_tot))
stopifnot("Some algorithm(s) use both IADL operationalisations!" = continue)
```

@@

```{r}
#| label: "kappas"

# Prepare combinations within IADL operationalisation:
kappas <- lapply(set_names(names(algos)), function(o) {
  combn(algos[[o]], 2) |>
      t() |>
      as_tibble() |>
      `colnames<-`(c("predictor", "reference")) |>
      left_join(conc$table, by = join_by(predictor, reference)) |>
      pull(Kappa_raw)
})

# Add cross-operationalisation cases
kappas$cross <- subset(conc$table, predictor %in% algos$faq_9 & reference %in% algos$faq_tot)$Kappa_raw

# Extract Kappa summaries:
kappa_sums <- sapply(names(kappas), function(i) {
  paste0(do_summary(kappas[[i]], 2, "M"),", SD = ", do_summary(kappas[[i]], 2, "SD"))
})

# Add Kappa summaries of algos with same everything but different IADL:
kappa_iadl <- data.frame(
  predictor = c("Lvl.II (1)", "MMSE (1)", "MMSE (3)", paste0("MoCA (",seq(1,59,2),")"), "sMoCA (1)"),
    reference = c("Lvl.II (2)", "MMSE (2)", "MMSE (4)", paste0("MoCA (",seq(2,60,2),")"), "sMoCA (2)")
) |>
  left_join(conc$table) |>
  pull(Kappa_raw)

kappa_iadl_sums <- paste0(do_summary(x = kappa_iadl, 2, "M"),", SD = ", do_summary(x = kappa_iadl, 2, "SD"))
```

Results of the analyses of prediction Accuracy, Cohen's $\kappa$, Sensitivity and Specificity are presented in @fig-acc, @fig-kappa, @fig-sens and @fig-spec respectively. **Numerical results are available at ...** [^2]. Generally, algorithms that employed the same operationalization of IADL deficit showed substantial pairwise concordance, however, algorithms that operationalized IADL deficit differently did not. Whereas among algorithms with identical IADL deficit operationalization, the agreement judged by Cohen's $\kappa$ was moderately high (operationalization by FAQ total score: $\kappa$ = `r kappa_sums["faq_tot"]`; operationalization by FAQ item 9: $\kappa$ = `r kappa_sums["faq_9"]`), among algorithms that differ in IADL deficit operationalization but are otherwise identical it was low: $\kappa$ = `r kappa_iadl_sums`.

>>>>

desc <- tar_read(sample_description, store = upstore)
rates <- tar_read(rate_summaries, store = upstore)
algos <- tar_read(algorithms, store = upstore)
pred <- tar_read(demographic_predictors, store = upstore)
conc <- tar_read(concordance_statistics, store = upstore)
kappa <- tar_read(kappa_summmaries, store = upstore)
perc <- rates$table$perc

@@

# Minimum p-value of logistic regressions:
min_p <- subset(pred$values, quantity == "p-value")$estimate |>
  min() |>
  do_summary(3, "p")
```

@@

Results of the analyses of prediction Accuracy, Cohen's $\kappa$, Sensitivity and Specificity are presented in @fig-acc, @fig-kappa, @fig-sens and @fig-spec respectively. **Numerical results are available at ...** [^2]. Generally, algorithms that employed the same operationalization of IADL deficit showed substantial pairwise concordance, however, algorithms that operationalized IADL deficit differently did not. Whereas among algorithms with identical IADL deficit operationalization, the agreement judged by Cohen's $\kappa$ was moderately high (operationalization by FAQ total score: $\kappa$ = `r kappa$sums["faq_tot"]`; operationalization by FAQ item 9: $\kappa$ = `r kappa$sums["faq_9"]`), among algorithms that differ in IADL deficit operationalization but are otherwise identical it was low: $\kappa$ = `r kappa$sums["iadl"]`.
